Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-26 tex/MesnardoBarba2019.tex
Remove listings language

\usepackage{listings}
\lstset{
    aboveskip=20pt,
    belowskip=20pt,
    lineskip=5pt,
    backgroundcolor=\color{white},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=true,
    breaklines=true,
    captionpos=none,
    extendedchars=true,
    frame=none,
    keepspaces=true,
    language=bash,
    morekeywords={*,...},
    numbers=none,
    numbersep=5pt,
    rulecolor=\color{black},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    stepnumber=2,
    tabsize=2,
    title=\lstname,
}

@@

\begin{lstlisting}[float]
$ cd $CLOUDREPRO/docker/petibm
$ docker build --tag=barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu --file=Dockerfile .
$ docker push barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu
\end{lstlisting}

>>>>

\usepackage{listings}
\lstset{
    aboveskip=20pt,
    belowskip=20pt,
    lineskip=5pt,
    backgroundcolor=\color{white},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=true,
    breaklines=true,
    captionpos=none,
    extendedchars=true,
    frame=none,
    keepspaces=true,
    morekeywords={*,...},
    numbers=none,
    numbersep=5pt,
    rulecolor=\color{black},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    stepnumber=2,
    tabsize=2,
    title=\lstname,
}

@@

\begin{lstlisting}
$ cd $CLOUDREPRO/docker/petibm
$ docker build --tag=barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu --file=Dockerfile .
$ docker push barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu
\end{lstlisting}
